\documentclass[a4paper, 11pt]{article}

%\usepackage[swedish]{babel}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\fancyhf{} %clears default header and footer
\lhead{DD2380 Artificial Intelligence}
\rhead{Proj. report gr.41}
\cfoot{Page \thepage\ of \pageref{LastPage}}
\pagestyle{fancy}
\usepackage{lastpage}
%\usepackage{natbib}
%\usepackage{amsmath}


\begin{document}
\begin{titlepage}
\begin{center}
{\Huge \noindent Royal Institute of Technology KTH}
\vspace{15pt}\ 
{\huge \noindent DD2380 Artificial Intelligence}
\vspace{3cm}
\hrule
\vspace{15pt}
{\Huge Word predictor functionality: an evaluation study}
\vspace{15pt}
\hrule
\vspace{1cm}
{\Large\today\\}
\vspace{1em}
{\slshape Jonathan Kindfält, Johannes Olsson,
\\*Mikael Sjöberg, Alexander Östman}
\end{center}
\vspace{1cm}
\paragraph{Abstract}
Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text.Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text.Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text. Some text.Some text. Some text.

\end{titlepage}

\section{Introduction}
This is just a sentence to make a reference to \cite{frey}. Without it, there is no bibliography section.

\bibliographystyle{ieeetr}
\bibliography{sources}

\end{document}